---
title: "Lisbon_data"
author: "Catarina Pien"
date: "June 6, 2019"
output: html_document
---

Clear the environment.
```{r clear, include = FALSE}
rm(list=ls(all=TRUE))
```



## 1.Setup and Download Libraries

```{r setup, include = FALSE, warning = FALSE, message = FALSE}

rm(list=ls(all=TRUE))

library(readr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyr)
library(gridExtra)
library(stringr)
library(kableExtra)
library(knitr)
library(hms)
```

## 2.Load Data, Check Variable Types

```{r load, include = FALSE, warning = FALSE, message = FALSE}
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/Database/R_code/")
phys <- read_csv("Data/TblPhysicalData.csv")

# Add and change data and time formats
phys$Date<-as.Date(phys$Date,"%m/%d/%Y")
phys$Time <- as.hms(phys$Time)
phys$Year <- ordered(year(phys$Date))
phys$Month <- ordered(month(phys$Date))
mymonths <- c("Jan","Feb","Mar",
              "Apr","May","Jun",
              "Jul","Aug","Sep",
              "Oct","Nov","Dec")
#add abbreviated month name
phys$MonthAbb <- mymonths[ phys$Month ]
#set order of months
phys$MonthAbb <-ordered(phys$MonthAbb,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))

```

## 3.Check variables to include in QC, reorganize the data frame.
```{r filter, include = FALSE, message = FALSE, warning = FALSE}

summary(phys$PhysicalDataID)
unique(phys$`Station Code`)
unique(phys$Recorder) # All NA
summary(phys$`Field Check`)
unique(phys$Tide) # All NA
unique(phys$DataCorrectionComments)
unique(phys$`YSI #`)

# Rename some columns, remove unnecessary columns
phys.s <- phys %>%
  rename(StationCode = `Station Code`,
         WTemp = WaterTemperature,
         Secchi = SecchiDiskDepth) %>%
  select(-c(Recorder, `Field Check`, Crew, Tide, EnteredBy, `QA/QC'dBy`, `YSI #`,
            LightData, DriftData, LarvalData, ZoopsData, `50_ZoopsData`, ChlData, PhytoData, NutrData,
            Comments, DataCorrectionComments, StartMeter, EndMeter, MeterSetTime))

```


## 4. Edit "bad" data and revisualize data
```{r Remove bad data, include= FALSE, warning = FALSE, message = FALSE}
# Edits to data
to_drop <- c(1575, 1631, 1632, 1722, 1724, 1867, 1308, 748)

# To change
phys.s$WTemp[phys.s$WTemp == 62] <- 16.7
phys.s$WTemp[phys.s$WTemp == 0.169] <- 16.9
phys.s$Turbidity[phys.s$PhysicalDataID==680] <- 15.4
phys.s$Turbidity[phys.s$PhysicalDataID==656] <- 94.2
phys.s$EC[phys.s$PhysicalDataID==748] <- 732
phys.s$EC[phys.s$PhysicalDataID==926] <- 1284
phys.s$EC[phys.s$PhysicalDataID==1847] <- 170
phys.s$SpCnd[phys.s$PhysicalDataID==1140] <- 848
phys.s$SpCnd[phys.s$PhysicalDataID==1139] <- 889
phys.s$SpCnd[phys.s$PhysicalDataID==1847] <- 101
phys.s$Secchi[phys.s$PhysicalDataID==708] <- NA
phys.s$DO[phys.s$PhysicalDataID==1409] <- NA
phys.s$pH[phys.s$PhysicalDataID==1501] <- 7.92

phys.s$StationCode[phys.s$PhysicalDataID==1752] <- "STTD"
phys.s$EC[phys.s$PhysicalDataID==1752] <- 530
phys.s$SpCnd[phys.s$PhysicalDataID==1752] <- 563
phys.s$pH[phys.s$PhysicalDataID==1752] <- 8.13
phys.s$Turbidity[phys.s$PhysicalDataID==1752] <- 16.5
phys.s$Tide[phys.s$PhysicalDataID==1752] <- "Ebb"
phys.s$Date[phys.s$PhysicalDataID==1752] <-as.Date("2018-09-27", format = "%Y-%m-%d")

phys.s$Time[phys.s$PhysicalDataID==401] <- as.hms("13:22:00", "%H:%m:%S")
phys.s$Time[phys.s$PhysicalDataID==1602] <- as.hms("13:50:00", "%H:%m:%S")

#add datetime
phys.s <- phys.s%>%
  mutate(Datetime = paste(Date, Time))
phys.s$Datetime = as.POSIXct(phys.s$Datetime, 
                           format = "%Y-%m-%d %H:%M:%S")

# Remove rows with no data
phys.s <- phys.s%>%
  filter(!PhysicalDataID %in% to_drop)

```


## 4a) Plot edited YBFMP/Fall Flow data

```{r Plots Overview, echo = FALSE, message = FALSE, warning = FALSE}
p.temp <- ggplot(phys.s, aes(Date, WTemp)) + geom_point() + labs(y = "Water Temp(C)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.secchi <- ggplot(phys.s, aes(Date, Secchi)) + geom_point() + labs(y = "Secchi Depth(m)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.ec <- ggplot(phys.s, aes(Date, EC)) + geom_point() + labs(y = "EC(useimens/cm)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.spc <- ggplot(phys.s, aes(Date, SpCnd)) + geom_point() + labs(y = "SpCnd(useimens/cm)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.pH <- ggplot(phys.s, aes(Date, pH)) + geom_point() + labs(y = "pH") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.do <- ggplot(phys.s, aes(Date, DO)) + geom_point() + labs(y = "DO(mg/L)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.turb <- ggplot(phys.s, aes(Date, Turbidity)) + geom_point() + labs(y = "Turbidity(NTU)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))

# Arrange plots together
grid.arrange(p.temp, p.ec, p.spc, p.secchi, p.turb, p.do, p.pH)
```

## 5.Separate into separate datasets: Yolo, LIS, SHR, STTD, Fall Flow (FF), YTR, CCS, KNA 

```{r Station datasets, include = FALSE, message = FALSE, warning = FALSE}
phys_CCS <- phys.s %>%
  filter(StationCode == "CCS")

phys_KNA <- phys.s %>%
  filter(StationCode == "KNA")

phys_Yolo <- phys.s%>%
  filter(StationCode == "STTD" | StationCode == "LIS" | StationCode == "SHR")

phys_STTD <- phys.s %>%
  filter(StationCode == "STTD")

phys_SHR <- phys.s%>%
  filter(StationCode == "SHR")

phys_LIS <- phys.s%>%
  filter(StationCode == "LIS")

phys_YTR <- phys.s %>%
  filter(str_detect(StationCode, "^YTR"))

phys_FF <- phys.s %>%
  filter(StationCode != "STTD" & StationCode != "SHR" & StationCode != "LIS" & StationCode != "CCS" & StationCode !="KNA") %>%
  filter(!str_detect(StationCode, "^YTR"))

```

## 6. Look at summary tables - Min and max of variables by station

```{r minmaxtables, message = FALSE, warning = FALSE}

# All database data
WQ.overall <- phys.s %>%
  summarize(min.temp = min(WTemp, na.rm=T),
            max.temp = max(WTemp, na.rm=T),
            min.EC = min(EC, na.rm=T),
            max.EC = max(EC,na.rm=T),
            min.SPC = min(SpCnd,na.rm=T),
            max.SPC = max(SpCnd,na.rm=T),
            min.Secchi = min(Secchi,na.rm=T),
            max.Secchi = max(Secchi,na.rm=T),
            min.Turbidity = min(Turbidity,na.rm=T),
            max.Turbidity = max(Turbidity,na.rm=T),
            min.pH = min(pH,na.rm=T),
            max.pH = max(pH,na.rm=T),
            min.DO = min(DO,na.rm=T),
            max.DO = max(DO,na.rm=T),
            n = n()) 

WQ1.sum <- phys.s %>%
  group_by(StationCode) %>%
  summarize(min.temp = min(WTemp, na.rm=T),
            max.temp = max(WTemp, na.rm=T),
            min.EC = min(EC, na.rm=T),
            max.EC = max(EC,na.rm=T),
            min.SPC = min(SpCnd,na.rm=T),
            max.SPC = max(SpCnd,na.rm=T),
            n = n())

WQ2.sum <- phys.s %>%
  group_by(StationCode) %>%
  summarize(min.Secchi = min(Secchi,na.rm=T),
            max.Secchi = max(Secchi,na.rm=T),
            min.Turbidity = min(Turbidity,na.rm=T),
            max.Turbidity = max(Turbidity,na.rm=T),
            min.pH = min(pH,na.rm=T),
            max.pH = max(pH,na.rm=T),
            min.DO = min(DO,na.rm=T),
            max.DO = max(DO,na.rm=T),
            n = n())

kable(WQ.overall) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

kable(WQ1.sum) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

kable(WQ2.sum) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```


## 6. Check against Lisbon data

#### Yolo
```{r Lisbon Check Yolo, echo = FALSE, message = FALSE, warning = FALSE}
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/Database/R_code/")
#Sensors
  #Water Temp in F =25  (2008)
  #DO= 61  (2013)
  #EC = 100  (2013)
  #pH =62   (2013)
  #Turbidity =27  (2013)

# Read files (came from cdec4gov)
LIS_WTemp <- read_csv("Data/STA/LIS_25.csv")
LIS_DO <- read_csv("Data/STA/LIS_61.csv")
LIS_pH <- read_csv("Data/STA/LIS_62.csv")
LIS_Turb <- read_csv("Data/STA/LIS_27.csv")
LIS_EC <- read_csv("Data/STA/LIS_100.csv")

# Make edits and select just the relevant columns
LIS_WTemp_ed <- LIS_WTemp %>%
  select(5,6) %>%
  filter(VALUE<99998) %>% # Remove these non-values
  mutate(Temp_C = round((VALUE-32)*5/9,1)) #Change to Celsius
LIS_DO_ed <- LIS_DO %>%
  select(5,6) %>%
  rename("DO" = VALUE)
LIS_pH_ed <- LIS_pH %>%
  select(5,6) %>%
  rename("pH" = VALUE)
LIS_Turb_ed <- LIS_Turb %>%
  select(5,6) %>%
  rename("Turbidity" = VALUE)
LIS_EC_ed <- LIS_EC%>%
  select(5,6) %>%
  rename(EC = "VALUE")

# Merge variables together (2 at a time!)
a <- merge(LIS_DO_ed, LIS_Turb_ed, by = "DATE TIME")
b <- merge(a, LIS_EC_ed, by = "DATE TIME")
c <- merge(b, LIS_pH_ed, by = "DATE TIME")
LIS_WQ <- left_join(LIS_WTemp_ed, c, by = "DATE TIME")

# Add some date time variables for filtering
LIS_WQ$Time <- strftime(LIS_WQ$`DATE TIME`, format = "%H:%M:%S")
LIS_WQ$Date <- as.Date(LIS_WQ$`DATE TIME`)
LIS_WQ$Hour <- as.numeric(format(strptime(LIS_WQ$Time, "%H:%M:%S"), "%H"))

# Edit merged table with the tiniest of QC
LIS_WQ_f <- LIS_WQ %>%
  rename(Datetime = `DATE TIME`,
         WTemp = Temp_C) %>%
  filter(Hour>06 & Hour<15)%>%
  filter(WTemp>0 & WTemp<40) %>%
  filter(EC>0) %>%
  filter(DO>0) %>%
  filter(pH>0 & pH<14) %>%
  filter(Turbidity >0) %>%
  mutate(StationCode="LIS_RT") %>%
  select(1,3:9,11)

# Plot each variable (LIS alone)
Temp <- ggplot(LIS_WQ_f, aes(Datetime, WTemp)) + geom_point() + theme_bw()
DO <- ggplot(LIS_WQ_f, aes(Datetime, DO)) + geom_point() + theme_bw()
pH <- ggplot(LIS_WQ_f, aes(Datetime, pH)) + geom_point() + theme_bw()
Turb <- ggplot(LIS_WQ_f, aes(Datetime, Turbidity)) + geom_point() + theme_bw()
EC <- ggplot(LIS_WQ_f, aes(Datetime, EC)) + geom_point() + theme_bw()

grid.arrange(Temp, DO, pH, Turb, EC, nrow = 2)

# Bring Yolo data in, arrange columns in the same way so we can bind
Yolo_WQ <- phys_Yolo %>%
  select(Datetime,WTemp, DO, Turbidity, EC, pH, Time, Date, StationCode)

WQ_large <- rbind(LIS_WQ_f, Yolo_WQ)
WQ_large$Year <- as.numeric(year(WQ_large$Date))
WQ_sub <- WQ_large %>%
  filter(Year>2001)
WQ_sub2 <- WQ_large %>%
  filter(Year>2006)
WQ_sub3 <- WQ_large %>%
  filter(Year>2010)

# Plot with LIS (blue) and Yolo (other light colors)
ggplot(WQ_large, aes(Datetime, WTemp,colour = StationCode)) + geom_point() + theme_bw() +
  scale_colour_manual(values = c("#F3B2FF", "#106E83", "#FFC971", "#BAFF87")) + 
  labs(title = "Water Temperature")+theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

ggplot(WQ_sub, aes(Datetime, EC,colour = StationCode)) + geom_point() + theme_bw() +
  scale_colour_manual(values = c("#F3B2FF", "#106E83", "#FFC971", "#BAFF87")) + 
  labs(title = "EC")+theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

ggplot(WQ_sub2, aes(Datetime, DO, colour = StationCode)) + geom_point() + theme_bw() +
  scale_colour_manual(values = c("#F3B2FF", "#106E83", "#FFC971", "#BAFF87")) + 
  labs(title = "DO")+theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

ggplot(WQ_sub2, aes(Datetime, pH,colour = StationCode)) + geom_point() + theme_bw() +
  scale_colour_manual(values = c("#F3B2FF", "#106E83", "#FFC971", "#BAFF87")) + 
  labs(title = "pH")+theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

ggplot(WQ_sub3, aes(Datetime, Turbidity,colour = StationCode)) + geom_point() + theme_bw() +
  scale_colour_manual(values = c("#F3B2FF", "#106E83", "#FFC971", "#BAFF87")) + 
  labs(title = "Turbidity")+theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

```

#### Fall Flow
```{r Lisbon Check Fall Flow, echo = FALSE, message = FALSE, warning = FALSE}
FF_WQ <- phys_FF %>%
  select(Datetime,WTemp, DO, Turbidity, EC, pH, Time, Date, StationCode)

WQ_large_FF <- rbind(LIS_WQ_f, FF_WQ)
WQ_large_FF$Year <- as.numeric(year(WQ_large_FF$Date))
WQ_sub_FF <- WQ_large_FF %>%
  filter(Year>2001)
WQ_sub2_FF <- WQ_large_FF %>%
  filter(Year>2006)
WQ_sub3_FF <- WQ_large_FF %>%
  filter(Year>2011)

ggplot(WQ_large_FF, aes(Datetime, WTemp,colour = StationCode)) + geom_point() + theme_bw() +
  scale_colour_manual(values = c("#F3B2FF","#FFC971", "#FA8FFF", "#62FF62","#030C5C","#EFFF4F","#FFE4EA", "#E3B5FF" ,"#B5D7FF", "#B5FFFF", "#C2C1CB", "#C2C1CB")) +  
  labs(title = "Water Temperature")+theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

ggplot(WQ_sub3_FF, aes(Datetime, EC,colour = StationCode)) + geom_point() + theme_bw() +
  scale_colour_manual(values = c("#F3B2FF","#FFC971", "#FA8FFF", "#62FF62","#030C5C","#EFFF4F","#FFE4EA", "#E3B5FF" ,"#B5D7FF", "#B5FFFF", "#C2C1CB", "#C2C1CB")) + 
  labs(title = "EC")+theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

ggplot(WQ_sub3_FF, aes(Datetime, DO, colour = StationCode)) + geom_point() + theme_bw() +
  scale_colour_manual(values = c("#F3B2FF","#FFC971", "#FA8FFF", "#62FF62","#030C5C","#EFFF4F","#FFE4EA", "#E3B5FF" ,"#B5D7FF", "#B5FFFF", "#C2C1CB", "#C2C1CB")) +  
  labs(title = "DO")+theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

ggplot(WQ_sub3_FF, aes(Datetime, pH,colour = StationCode)) + geom_point() + theme_bw() +
 scale_colour_manual(values = c("#F3B2FF","#FFC971", "#FA8FFF", "#62FF62","#030C5C","#EFFF4F","#FFE4EA", "#E3B5FF" ,"#B5D7FF", "#B5FFFF", "#C2C1CB", "#C2C1CB")) + 
  labs(title = "pH")+theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

ggplot(WQ_sub3_FF, aes(Datetime, Turbidity,colour = StationCode)) + geom_point() + theme_bw() +
   scale_colour_manual(values = c("#F3B2FF","#FFC971", "#FA8FFF", "#62FF62","#030C5C","#EFFF4F","#FFE4EA", "#E3B5FF" ,"#B5D7FF", "#B5FFFF", "#C2C1CB", "#C2C1CB")) + 
  labs(title = "Turbidity")+theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))
```

