---
title: "Zoop_QAQC"
author: "Catarina Pien"
date: "May 23, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 10000)
```

## 1.Setup and Download Libraries

```{r setup, results=FALSE, warning = FALSE, message = FALSE}

rm(list=ls(all=TRUE))

library(tidyverse)
library(lubridate)
library(stringr)
library(here)
library(kableExtra)
library(data.table)
library(scales)
```

## 2.Load Data tables, Change datetime formats, Rename variables, Check Variable Types

```{r load, results = FALSE, warning = FALSE, message = FALSE}
# Load data - several tables
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/Database/R_code/")
phys <- read.csv("Data/QC/LT_phys_qc.csv")
zoop_catch <- read.csv("Data/TblZoopsCatchData.csv")
zoop_ref <- read.csv("Data/TblZooplankton.csv")
zoop_tax <- read.csv("Data/YB_TaxonomyTable.csv")


# Add and change date formats
phys$SampleDate<-as.Date(phys$SampleDate,format ="%Y-%m-%d")
phys$Year <- ordered(year(phys$SampleDate))
phys$Month <- ordered(month(phys$SampleDate))
phys$MonthAbb <-ordered(phys$MonthAbb,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))
phys$Datetime = as.POSIXct(phys$Datetime, format = "%Y-%m-%d %H:%M:%S")

# Some renaming 
zoop_ref <- zoop_ref %>%
  rename(`150_ZoopStartMeter`= X150_ZoopStartMeter,
         `50_ZoopStartMeter`= X50_ZoopStartMeter,
         `150_ZoopEndMeter`= X150_ZoopEndMeter,`50_ZoopEndMeter`= X50_ZoopEndMeter,
         `50_StartTime`= X50_StartTime,`50_StopTime`= X50_Stoptime,
         `150_SetTime`= X150SetTime,`50_SetTime`= X50_SetTime,
         `50_VolMeso` = X50_VolMeso, `50_SubMeso` = X50_SubMeso,
         `50_VolMicro` = X50_VolMicro, `50_SubMicro` = X50_SubMicro)

```

## 3.Check variables, Clean up some columns

```{r filter, results = FALSE, message = FALSE, warning = FALSE}
str(phys)
str(zoop_catch)

summary(phys$PhysicalDataID)
unique(zoop_catch$Classification)
unique(zoop_catch$Organism)
unique(zoop_catch$OrganismID)
unique(zoop_catch$ZoopNetType)

# Get rid of a few columns
zoop_catch <- zoop_catch[,c(1:3,4:6)]
phys$Date <- NULL
```

## 4. Make changes that need to be made to data

```{r QC, message = FALSE, warning = FALSE}
#Organism related - change duplicates of organisms to the same Organism ID. This needs to be done in both
#taxonomy and catch tables.
zoop_catch$OrganismID[zoop_catch$OrganismID==114] <- 102
zoop_catch$OrganismID[zoop_catch$OrganismID==113] <- 95
zoop_catch$OrganismID[zoop_catch$OrganismID==66] <- 3
zoop_catch$OrganismID[zoop_catch$OrganismID==67] <- 33
zoop_catch$OrganismID[zoop_catch$OrganismID==75] <- 31
zoop_catch$OrganismID[zoop_catch$OrganismID==79] <- 9
zoop_catch$OrganismID[zoop_catch$OrganismID==71] <- 58

# yb_tax$OrganismID[yb_tax$OrganismID==114] <- 102
# yb_tax$OrganismID[yb_tax$OrganismID==113] <- 95
# yb_tax$OrganismID[yb_tax$OrganismID==66] <- 3
# yb_tax$OrganismID[yb_tax$OrganismID==67] <- 33
# yb_tax$OrganismID[yb_tax$OrganismID==75] <- 31
# yb_tax$OrganismID[yb_tax$OrganismID==79] <- 9
# yb_tax$OrganismID[yb_tax$OrganismID==71] <- 58

# Change spellings
yb_tax$Organism[yb_tax$Organism=="Acanthocyclops Vernalis copepodid"] <- "Acanthocyclops vernalis copepodid"
#yb_tax$Organism[yb_tax$Organism=="Acanthocyclops Vernalis"] <- "Acanthocyclops vernalis"

# write updated taxonomy table
# write.csv(yb_tax, "R_write/Zoop_tax_QC.csv")

# Two records mislabeled as OrganismID = 68 (an old code) - change to 64
zoop_catch$OrganismID[zoop_catch$ZoopsDataID==882] <- 64
zoop_catch$OrganismID[zoop_catch$ZoopsDataID==1005] <- 64

# Add ZoopNetType to a few entries
zoop_catch$ZoopNetType[zoop_catch$ZoopsCatchID==8663] <- 50
zoop_catch$ZoopNetType[zoop_catch$ZoopsCatchID==8664] <- 50
zoop_catch$ZoopNetType[zoop_catch$ZoopsCatchID==8665] <- 50
zoop_catch$ZoopNetType[zoop_catch$ZoopsCatchID==9829] <- 50
zoop_catch$ZoopNetType[zoop_catch$ZoopsCatchID==10375] <- 50

# Change Flowmeter Values. Other changes have been made in database. 
zoop_ref$`50_ZoopEndMeter`[zoop_ref$ZoopsDataID==799] <- 990000
zoop_ref$`50_ZoopEndMeter`[zoop_ref$ZoopsDataID %in% c(955,968,1000)] <- 1000000

# Remove a row (incorrect duplicate data)
zoop_ref <- zoop_ref %>%
  filter(ZoopsDataID != 766)

# Calculate difference between Start and End flowmeter
zoop_ref <- zoop_ref %>%
  mutate(`150_Flowdiff` = (`150_ZoopEndMeter`-`150_ZoopStartMeter`),
    `50_Flowdiff` = (`50_ZoopEndMeter`-`50_ZoopStartMeter`))

```

## 5. Merge data tables, calculate CPUE, rearrange variables

```{r cpue, message = FALSE, warning = FALSE}
# Merge datasets for CPUE variables
catch_zoop0 <- inner_join(zoop_ref, zoop_catch, by = "ZoopsDataID")
catch_zoop <- left_join(catch_zoop0, zoop_tax, by = "OrganismID")

# Fill in "ZoopNetType" as 150 for all that are not entered
catch_zoop$ZoopNetType[is.na(catch_zoop$ZoopNetType)] <- 150
  
# Calculate CPUE (Count/(S/V))
# CPUE differs based on flowmeter used, net size, and meso vs. microzooplankton
  # First calculate the volumes:
    # Volume sampled = (pi * diameter^2/4) * (Flowdiff * rotor constant/999999))
    # Subsample correction = (volume subsampled * #subsamples/ volume sent to contractors)

cz1 <- catch_zoop %>%
  mutate(`50_V_reg` = (pi*0.25/4)*(`50_Flowdiff`*26873/999999),
         `50_V_low` = (pi*0.25/4)*(`50_Flowdiff`*57560/999999),
         `150_V_reg` = (pi*0.25/4)*(`150_Flowdiff`*26873/999999),
         `150_V_low` = (pi*0.25/4)*(`150_Flowdiff`*57560/999999),
         `50_S_micro` = catch_zoop$`50_SubMicro` * catch_zoop$`Subsample.`/catch_zoop$`50_VolMicro`,
         `50_S_meso`  = catch_zoop$`50_SubMeso` * catch_zoop$`Subsample.`/catch_zoop$`50_VolMeso`,
         `150_S_micro` = catch_zoop$`SubMicro` * catch_zoop$`Subsample.`/catch_zoop$`VolMicro`,
         `150_S_meso`  = catch_zoop$`SubMeso` * catch_zoop$`Subsample.`/catch_zoop$`VolMeso`) %>%
mutate(CPUE = ifelse((ZoopNetType == 50 & FlowMeterSpeed == "Regular" & Classification == "Microzooplankton & Nauplii"), 
                            round(((Count/`50_S_micro`) /`50_V_reg`),3), 
         ifelse((ZoopNetType == 50 & FlowMeterSpeed == "Regular" & Classification != "Microzooplankton & Nauplii"), 
                round(((Count/`50_S_meso`)/`50_V_reg`),3),
         ifelse((ZoopNetType == 50 & FlowMeterSpeed == "Low" & Classification != "Microzooplankton & Nauplii"),
                round(((Count/`50_S_meso`)/`50_V_low`),3),
         ifelse((ZoopNetType == 50 & FlowMeterSpeed == "Low" & Classification == "Microzooplankton & Nauplii"),
                round(((Count/`50_S_micro`)/ `50_V_low`),3),
         ifelse((ZoopNetType == 150 & FlowMeterSpeed == "Regular" & Classification == "Microzooplankton & Nauplii"), 
                            round(((Count/`150_S_micro`) * `150_V_reg`),3), 
         ifelse((ZoopNetType == 150 & FlowMeterSpeed == "Regular" & Classification != "Microzooplankton & Nauplii"), 
                round(((Count/`150_S_meso`)/`150_V_reg`),3),
         ifelse((ZoopNetType == 150 & FlowMeterSpeed == "Low" & Classification != "Microzooplankton & Nauplii"),
                round(((Count/`150_S_meso`)/`150_V_low`),3),
         ifelse((ZoopNetType == 150 & FlowMeterSpeed == "Low" & Classification == "Microzooplankton & Nauplii"),
                round(((Count/`150_S_micro` )/ `150_V_low`),3),NA)))))))))


# Merge physical data
zoop_all_0 <- inner_join(phys,cz1, by = "PhysicalDataID") %>% 
  mutate(OrganismID = replace(OrganismID, OrganismID==68 & Year>2013, 64))


# Rename some columns, remove unnecessary columns
zoop_all_2 <- zoop_all_0 %>%
  dplyr::select(-c(MicrocystisVisualRank, StartTime:`50_StopTime`, EnteredBy:SlideCount, 
             ZoopsCatchID, ZoopsCode,
            `50_V_reg`, `50_V_low`, `150_V_reg`, `150_V_low`, `50_S_micro`, `50_S_meso`, `150_S_micro`, `150_S_meso`)) %>%
  rename(`150_VolMicro`= VolMicro,
         `150_SubMicro`= SubMicro,
         `150_VolMeso`= VolMeso,
         `150_SubMeso`=SubMeso,
         GearConditionCode = ConditionCode)


# Rearrange columns
zoop_all <- zoop_all_2[, c("PhysicalDataID", "ZoopsDataID",
                         "SampleDate", "Year", "Month", "MonthAbb", "Datetime", "SampleTime", "StationCode",
                         "WeatherCode", "Tide", "WaterTemperature", "Secchi", "Conductivity", "SpCnd", "pH", "DO","Turbidity",
                         "GearConditionCode","FieldComments", "LabComments",
                         "FlowMeterSpeed", "150_SetTime", "50_SetTime",
                         "150_ZoopStartMeter", "150_ZoopEndMeter", "50_ZoopStartMeter", "50_ZoopEndMeter",
                         "150_Flowdiff", "50_Flowdiff",
                         "150_VolMeso", "150_SubMeso", "150_VolMicro", "150_SubMicro", 
                         "50_VolMeso", "50_SubMeso", "50_VolMicro", "50_SubMicro",
                         "Subsample.", "OrganismID", "Classification", "Organism", "Phylum",
                         "Subphylum", "Class", "Subclass", "Infraclass", "Superorder", "Order",
                        "Suborder", "Infraorder", "Superfamily", "Family", "Genus", "Species",
                         "TaxonName", "TaxonRank", "CommonName", "LifeStage", "Count", "ZoopNetType", "CPUE")]

zoop_all <- zoop_all %>%
  arrange(Year, Month,SampleTime, StationCode, ZoopNetType)

# Write file if you want
# write.csv(zoop_all, "R_write/zoop_merged.csv")

```

## 6. Pare down data to look at outliers

```{r Simplify data}
# Date format
zoop_all$SampleDate <- as.Date(zoop_all$SampleDate, format = "%m/%d/%y")

# Remove some variables, trim down to just SHR and STTD, adjust for years of interest
zoop_forreview <- zoop_all %>%
  filter(StationCode == "SHR" | StationCode == "STTD") %>%
  filter(Year != "2019") %>%
  dplyr::select(c(SampleDate, SampleTime, Year, Month, StationCode, GearConditionCode,
           WeatherCode, WaterTemperature, Secchi, Turbidity, Conductivity, SpCnd, pH, DO,
           Phylum, Subphylum, Class, Subclass, Infraclass,
           Superorder, Order, Suborder, Infraorder, Superfamily, Family, Genus, Species, 
           CommonName, TaxonName, TaxonRank, LifeStage, Classification, Organism,
           FlowMeterSpeed, `150_Flowdiff`, `50_Flowdiff`,  `150_SetTime`, `50_SetTime`, 
           ZoopNetType, Count, CPUE, 
           FieldComments, LabComments, ZoopsDataID))

zoop_forreview <- zoop_forreview %>%
  drop_na(CPUE)
zoop_forreview$ZoopNetType <- as.factor(zoop_forreview$ZoopNetType)
levels(zoop_forreview$ZoopNetType) <- c("50_micron", "150_micron")

zoop_pub <- zoop_forreview %>%
  dplyr::select(-c(FlowMeterSpeed:`50_SetTime`, ZoopsDataID)) %>%
  arrange(SampleDate, SampleTime, StationCode)

write.csv(zoop_pub, "R_write/Zoop_public.csv")

```


## 7a. Overview of data: net differences

```{r Organisms Plot, echo = FALSE, message = FALSE, warning = FALSE}

# Net type and year
ggplot(zoop_all, aes(Year, CPUE, fill = ZoopNetType)) + geom_col()

# Make some datasets
calanoid <- zoop_cpue %>% filter(Order == "Calanoida")
cladocera <- zoop_cpue %>% filter(Suborder == "Cladocera")
cyclopoid <- zoop_cpue %>% filter(Order == "Cyclopoida")
macro <- zoop_cpue %>% filter(Classification == "Macrozooplankton")
micro <- zoop_cpue %>% filter(Classification == "Microzooplankton & Nauplii")

# Look at organisms - CPUE 
ggplot(zoop_cpue, aes(x=Classification, y = CPUE, fill =NetType)) + 
  geom_col(position = "dodge") +
    scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) + labs(title = "Classification")+
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11),axis.title.x = element_blank(),axis.text.x = element_text(angle = 90, hjust = 1)) 

```

## 7b. Look at organisms by taxonomic categories
```{r Organisms Plot big, warning = FALSE, message = FALSE, fig.width=12, fig.height=16}

# Look at each taxonomic category
t1 <- ggplot(zoop_cpue, aes(x=Phylum, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="Sum CPUE by Phylum") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11),axis.title.x = element_blank(),
                    axis.text.x = element_text(angle = 90, hjust = 1)) 

t2 <- ggplot(zoop_cpue, aes(x=Class, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="Sum CPUE by Class") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11),axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

t3 <- ggplot(zoop_cpue, aes(x=Subclass, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="Sum CPUE by SubClass") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11),axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

zoop_order <- zoop_cpue %>%
  filter(!is.na(Order))
t4 <- ggplot(zoop_order, aes(x=Order, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="CPUE by Order") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11),axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

zoop_family <- zoop_cpue %>%
  filter(!is.na(Family))
t5 <- ggplot(zoop_family, aes(x=Family, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="CPUE by Family") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 9), axis.title = element_text(size = 11),axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

zoop_genus <- zoop_cpue %>%
  filter(!is.na(Genus))
t6 <- ggplot(zoop_genus, aes(x=Genus, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="CPUE by Genus") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 8), axis.title = element_text(size = 11),axis.title.x = element_blank(),axis.text.x = element_text(angle = 90, hjust = 1)) 

# Compare changes: Organism vs.Taxon
# Calanoid species
org1 <- ggplot(calanoid, aes(x=Organism, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") + labs(title = "Calanoid - Organism") +  
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

tax1 <- ggplot(calanoid, aes(x=TaxonName, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") + labs(title = "Calanoid - Taxon") +  
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

# Cladocera species
org2 <- ggplot(cladocera, aes(x=Organism, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Cladocera - Organism")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

tax2 <- ggplot(cladocera, aes(x=TaxonName, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Cladocera - Taxon")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 
# Cyclopoid species
org3 <- ggplot(cyclopoid, aes(x=Organism, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  labs(title = "Cylopoid - Organism")+
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

tax3 <- ggplot(cyclopoid, aes(x=TaxonName, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  labs(title = "Cylopoid - Taxon")+
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

# Macrozooplankton
org4 <- ggplot(macro, aes(x=Organism, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Macrozooplankton - Organism")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1))

tax4 <- ggplot(macro, aes(x=TaxonName, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Macrozooplankton - Taxon")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1))

# Microzooplankton
org5 <- ggplot(micro, aes(x=Organism, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Microzooplankton - Organism")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1))

tax5 <- ggplot(micro, aes(x=TaxonName, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Microzooplankton - Taxon")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1))

grid.arrange(t1, t2, t3, t4, t5, t6, ncol = 2)
grid.arrange(org1, org2, org3, org4, org5, ncol = 2)
grid.arrange(tax1, tax2, tax3, tax4, tax5, ncol = 2)
```


## 8. Summarize CPUE by sampling event/Net Type. Plot for each year. 
* Calculate mean, sd, median, IQR, ul, ll for each Year/Station/FlowMeterSpeed Combo. 

```{r Total CPUE, message = FALSE, warning = FALSE}

## Plots
ggplot(zoop_forreview, aes(SampleDate, CPUE, col = ZoopNetType))+geom_col()

########################################################
### Summarize CPUE per sampling event  for 150-micron
zoop_onefifty <- zoop_forreview %>%
  filter(ZoopNetType == "150_micron") %>%
  group_by(StationCode, Year, Month, SampleDate, FlowMeterSpeed, FieldComments, LabComments)%>%
  summarize(ZoopsDataID = median(ZoopsDataID),
            CPUE.total = sum(CPUE),
            catch.total = sum(Count),
            Flowdiff = median(`150_Flowdiff`),
            SetTime = median(`150_SetTime`))

zoop_onefifty$SampleDate <- as.Date(zoop_onefifty$SampleDate, format = "%m/%d/%y")
zoop_forreview$SampleDate <- as.Date(zoop_forreview$SampleDate, format = "%m/%d/%y")

#### Create plots of CPUE (these go into Plots folder)

# List of all of the plots (by station)
plist <- by(zoop_onefifty, zoop_onefifty$Year, function(i) {
  p <- ggplot(i)+
    geom_point(aes(SampleDate, CPUE.total)) +
    scale_x_date(breaks = "15 days", labels = date_format("%m/%d/%Y")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
})

# Automatically saves images in list (above) to your working directory folder.
lapply(names(plist), 
       function(x) ggsave(filename=paste("Plots/onefifty_",x,".png",sep=""), plot=plist[[x]], bg = "transparent"))


### Calculate median, IQR
onefifty.medians <- zoop_onefifty %>%
  group_by(StationCode, Year, FlowMeterSpeed) %>%
  summarize(CPUE.median = median(CPUE.total),
            Q1 = quantile(CPUE.total, probs = 0.25), 
            Q3 = quantile(CPUE.total, probs = 0.75),
            IQR = Q3-Q1,
            ul = Q3 + 1.5 * IQR,
            ll = Q1 - 1.5 * IQR,
            CPUE.mean = mean(CPUE.total),
            SD.CPUE = sd(CPUE.total),
            Flowdiff.mean = mean(Flowdiff),
            SD.Flowdiff = sd(Flowdiff),
            n = n())

### Join sample data with medians and mark "check" for anything over the upper limit or below CPUE of 200
onefiftycheck <- left_join(zoop_onefifty, onefifty.medians) %>%
  mutate(check = ifelse(CPUE.total > ul | Flowdiff <401 | Flowdiff > 10000, "Y", "N"),
         NetSize = "150_micron") %>%
  filter(check == "Y")%>%
  dplyr::select(-c(Q1,Q3))


##################################################
### Summarize CPUE per sampling event for 50-micron

zoop_fifty$SampleDate <- as.Date(zoop_fifty$SampleDate, format = "%m/%d/%y")

zoop_fifty <- zoop_forreview %>%
  filter(ZoopNetType == "50_micron")%>%
  #filter(CPUE<5000) %>%
  group_by(StationCode, Year, Month, SampleDate, FlowMeterSpeed, FieldComments, LabComments)%>%
  summarize(ZoopsDataID = median(ZoopsDataID),
            CPUE.total = sum(CPUE),
            catch.total = sum(Count),
            Flowdiff = median(`50_Flowdiff`),
            SetTime = median(`50_SetTime`))


#### Create plots of CPUE (these go into Plots folder)
# List of all of the plots (by station)
plist2 <- by(zoop_fifty, zoop_fifty$Year, function(i) {
  p2 <- ggplot(i)+
    geom_point(aes(SampleDate, CPUE.total)) +
    scale_x_date(breaks = "15 days", labels = date_format("%m/%d/%Y")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
})

# Automatically saves images in list (above) to your working directory folder.
lapply(names(plist2), 
       function(x) ggsave(filename=paste("Plots/fifty_",x,".png",sep=""), plot=plist2[[x]], bg = "transparent"))

### Calculate median, IQR for 50-zoop net
fifty.medians <- zoop_fifty %>%
  group_by(StationCode, Year, FlowMeterSpeed) %>%
  summarize(CPUE.median = median(CPUE.total),
            Q1 = quantile(CPUE.total, probs = 0.25), 
            Q3 = quantile(CPUE.total, probs = 0.75),
            IQR = Q3-Q1,
            ul = Q3 + 1.5 * IQR,
            ll = Q1 - 1.5 * IQR,
            CPUE.mean = mean(CPUE.total),
            SD.CPUE = sd(CPUE.total),
            Flowdiff.mean = mean(Flowdiff),
            SD.Flowdiff = sd(Flowdiff),
            n = n())

### Join sample data with medians and mark "check" for anything over the upper limit or below CPUE of 100
fiftycheck <- left_join(zoop_fifty, fifty.medians) %>%
  mutate(check = ifelse(CPUE.total > ul | Flowdiff <201 | Flowdiff >5000, "Y", "N"),
         NetSize = "50_micron") %>%
  filter(check == "Y")%>%
  dplyr::select(-c(Q1,Q3,ll))

```


### ANOVAs
```{r ANOVA}
library(car)

################# STTD ##################
### Plot data
zoop_150_sttd <- zoop_onefifty %>%
  filter(CPUE.total < 3000000) %>%
  filter(StationCode == "STTD") %>%
  mutate(Flowdiff_s = Flowdiff/SetTime)

zoop_150_sttd_reg <- zoop_150_sttd %>%
    filter(FlowMeterSpeed == "Regular")

zoop_150_sttd_low <- zoop_150_sttd %>%
    filter(FlowMeterSpeed == "Low")

# CPUE plots
ggplot(zoop_150_sttd_reg, aes(Year, CPUE.total))+geom_boxplot()

# Flowdiff/settime plots
ggplot(zoop_150_sttd_reg, aes(Year, Flowdiff_s))+geom_boxplot()


### Run ANOVAs
sttd.aov.cp.r <- aov(CPUE.total~Year, data = zoop_150_sttd_reg)
summary(sttd.aov.cp.r)

TukeyHSD(sttd.aov.cp.r)

####### CPUE Zoop_150_STTD_Reg #######
### Run ANOVAs
sttd.aov.cp.r <- aov(CPUE.total~Year, data = zoop_150_sttd_reg)
summary(sttd.aov.cp.r)

TukeyHSD(sttd.aov.cp.r)

### Check assumptions
# Homogeneity of variances
plot(sttd.aov.cp.r, 1)
leveneTest(CPUE.total ~ Year, data = zoop_150_sttd_reg)

  # Normality
plot(sttd.aov.cp.r, 2)
sttd_residuals_cp_r <- residuals(object = sttd.aov.cp.r)
shapiro.test(x = sttd_residuals )

######## Flowdiff Zoop_150_STTD_Reg #######

### Run ANOVAs
sttd.aov.f.r <- aov(Flowdiff_s~Year, data = zoop_150_sttd_reg)
summary(sttd.aov.f.r)

TukeyHSD(sttd.aov.f.r)

### Check assumptions

  # Homogeneity of variances
plot(sttd.aov.f.r, 1)
leveneTest(Flowdiff_s ~ Year, data = zoop_150_sttd_reg)

  # Normality
plot(sttd.aov.f.r, 2)
sttd_residuals_f_r <- residuals(object = sttd.aov.f.r)
shapiro.test(x = sttd_residuals_f_r)

######## CPUE Zoop_150_STTD_Low #######

ggplot(zoop_150_sttd_low, aes(Year, CPUE.total))+geom_boxplot()
ggplot(zoop_150_sttd_low, aes(Year, Flowdiff_s))+geom_boxplot()

### Run ANOVAs
sttd.aov.cp.l <- aov(CPUE.total~Year, data = zoop_150_sttd_low)
summary(sttd.aov.cp.l)

TukeyHSD(sttd.aov.cp.l)

### Check assumptions

  # Homogeneity of variances
plot(sttd.aov.cp.l, 1)
leveneTest(CPUE.total ~ Year, data = zoop_150_sttd_low)

  # Normality
plot(sttd.aov.cp.l, 2)
sttd_residuals_cp_l <- residuals(object = sttd.aov.cp.l)
shapiro.test(x = sttd_residuals_cp_l)

######## Flowdiff Zoop_150_STTD_Low #######

### Run ANOVAs
sttd.aov.f.l <- aov(Flowdiff_s~Year, data = zoop_150_sttd_low)
summary(sttd.aov.f.l)

TukeyHSD(sttd.aov.f.l)

### Check assumptions

  # Homogeneity of variances
plot(sttd.aov.f.l, 1)
leveneTest(Flowdiff_s ~ Year, data = zoop_150_sttd_low)

  # Normality
plot(sttd.aov.f.l, 2)
sttd_residuals_f_l <- residuals(object = sttd.aov.f.l)
shapiro.test(x = sttd_residuals_f_l)

################# SHR ##################

zoop_shr <- zoop_onefifty %>%
  filter(CPUE.total < 1000000)%>%
  filter(StationCode == "SHR")%>%
  filter(FlowMeterSpeed == "Low") %>%
  mutate(Flowdiff_s = Flowdiff/SetTime)

ggplot(zoop_shr, aes(Year, CPUE.total)) + geom_boxplot()
ggplot(zoop_shr, aes(Year, Flowdiff_s)) + geom_boxplot()

### Run ANOVA
shr.aov <- aov(Flowdiff_s~Year, data = zoop_shr)
summary(shr.aov)

TukeyHSD(shr.aov)
### Check assumptions

  # Homogeneity of variances
plot(shr.aov, 1) 
leveneTest(CPUE.total ~ Year, data = zoop_shr)

  # Normality
plot(shr.aov, 2)
shr_residuals <- residuals(object = shr.aov)
shapiro.test(x = shr_residuals )

### Kruskal-Wallis
kruskal.test(CPUE.total~Year, data = zoop_shr)


```


## 9. Look at Flowmeter data

```{r Flow, message = FALSE, warning = FALSE}

# Remove rows with no flowdiff value
Flowmeter <- zoop_all %>%
  gather(`150_Flowdiff`, `50_Flowdiff`, key = "NetType", value = "Flowdiff") %>%
  filter(!is.na(Flowdiff)) %>%
  filter(!is.na(FlowMeterSpeed))

# Histogram by net type
ggplot(Flowmeter, aes(Flowdiff)) + geom_histogram(binwidth = 500) +
  facet_wrap(~NetType) + theme_bw()

# Look at flow values by month
Flow_yr_month <- Flowmeter %>%
  group_by(NetType, Year, MonthAbb) %>%
  select(NetType,Year,MonthAbb,Flowdiff) %>%
  summarize(max.flow = max(Flowdiff),
            median.flow = median(Flowdiff),
            min.flow = min(Flowdiff))

# Look at flow values by month
Flow_month <- Flowmeter %>%
  group_by(NetType,MonthAbb) %>%
  summarize(max.flow = max(Flowdiff),
            median.flow = median(Flowdiff),
            min.flow = min(Flowdiff))

# Boxplots
ggplot(Flowmeter, aes(MonthAbb, Flowdiff)) + 
  geom_boxplot(fill = "#26bb11") + labs(title = "Boxplot: All Flows") + theme_bw() + facet_wrap(~NetType)

ggplot(Flow_yr_month, aes(MonthAbb, median.flow)) + geom_boxplot(fill = "#00acee") + 
  facet_wrap(~NetType) +labs(title = "Boxplot: Median flow over multiple years") + theme_bw()

# List of all flow diferences by station and date
Flow_sta_comments <- Flowmeter %>%
  filter(StationCode %in% c("STTD", "SHR")) %>%
  select(ZoopsDataID, StationCode, Year, SampleDate, MonthAbb, NetType, Flowdiff, FieldComments) %>%
  group_by(ZoopsDataID, StationCode, NetType,Year, SampleDate, MonthAbb, Flowdiff, FieldComments) %>%
  arrange(StationCode,NetType,Year,SampleDate,Flowdiff) %>%
  distinct(SampleDate,StationCode)

```

## 10. Calculate summary stats and IQR for flowmeter readings

```{r IQR Flowmeter}

# Calculate median, MAD, lower and upper ranges for each day
Flow.sum <- Flowmeter %>%
  filter(StationCode == "STTD" | StationCode == "SHR") %>%
  group_by(StationCode, NetType, FlowMeterSpeed) %>%
   summarize(min.Flowdiff = min(Flowdiff),
             max.Flowdiff = max(Flowdiff))

# Calculate median, MAD, lower and upper ranges for each day
Flow.IQR <- Flowmeter %>%
  filter(StationCode == "STTD" | StationCode == "SHR") %>%
  group_by(StationCode, NetType, FlowMeterSpeed) %>%
   summarize(Q1 = quantile(Flowdiff, probs = 0.25), 
            Q3 = quantile(Flowdiff, probs = 0.75),
            IQR = Q3-Q1,
            ul = Q3 + 1.5 * IQR,
            ll = Q1 - 1.5 * IQR)
kable(Flow.sum) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

kable(Flow.IQR) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

## 11. Read dayflow data
```{r incorporate dayflow}

dayflow <- read.csv("Data/Flow/Yolo_dayflow_compiled.csv")

# Extract date from flow dataset
dayflow <- dayflow %>%
  rename(SampleDate = Date) %>%
#mutate(Day = substr(Date, start = 1, stop = 2)) %>%
  #mutate(SampleDate = (paste(Year, Mo, Day, sep = "-"))) %>%
  arrange(Year)

dayflow$SampleDate <- as.Date(dayflow$SampleDate, format = "%Y-%m-%d")
dayflow$Month <- ordered(month(dayflow$SampleDate))
dayflow$Year <- ordered(dayflow$Year)
dayflow$Day <- as.character(day(dayflow$SampleDate))

# Look at flow data
ggplot(dayflow, aes(SampleDate, Flow)) + 
  geom_point()

ggplot(dayflow, aes(Month, Flow)) + 
  geom_boxplot()

# There are several repeats
dayflowF <- dayflow %>%
  distinct(SampleDate, .keep_all = TRUE)

# Combine 50-150 CPUE outliers with dayflow. 
checkoutliers <- rbind(fiftycheck,onefiftycheck)
checkoutliers$Day <- as.character(day(checkoutliers$SampleDate))
checkoutliers2 <- left_join(checkoutliers, dayflowF) %>%
  arrange(StationCode, SampleDate) %>%
  dplyr:: select(-c(Day, X, Mo, check, IQR, ll))

# Write outliers file
write.csv(checkoutliers2, "R_write/Checkzoopoutliers.csv")

```

## 12. Replace flagged values
```{r Replacement}

### Read in file with flags

zoop_flags <- read.csv("Checkzoopoutliers3.csv")

### Merge in flag, replace, mean, median values with zooplankton data

zoop_replace <- merge(zoop_all, checkoutliers) # Merge zooplankton data with the relevant mean and median values
zoop_replace_flag <- merge(zoop_replace, zoop_flags, by = "ZoopsDataID") # Merge data with flag and replace columns
zoop_flag_merge$Replace[is.na(zoop_flag_merge$Replace)] <- "N" # For data not in outlier files, fill "Replace" column with "N" 

### Replace incorrect values
# New column of flowdiffs. If replace = N, flowdiff does not change. If replace = Y, replace with the mean. 
zoop_edited <- zoop_flag_merge %>%
  mutate(Flowdiff2 = ifelse(Replace == "Y", Mean.CPUE, Flowdiff))

```


## Include variables relevant to EDI. 
```{r EDI/Public}
# EDI/Public

zoop_edi_catch <- zoop_edited %>%
  select(-c(`150_Flowdiff`, `50_Flowdiff`, ZoopsDataID)) %>%
  arrange(SampleDate, SampleTime, StationCode, ZoopNetType)

# Write file if you want
write.csv(zoop_edi_catch_2,"R_write/yolo_zoop_public.csv")
```

