---
title: "Zoop_QAQC"
author: "Catarina Pien"
date: "May 23, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 10000)
```

## 1.Setup and Download Libraries

```{r setup, results=FALSE, warning = FALSE, message = FALSE}

rm(list=ls(all=TRUE))

library(tidyverse)
library(lubridate)
library(stringr)
library(here)
library(kableExtra)
library(data.table)
library(scales)
```

## 2.Load Data tables, Change datetime formats, Rename variables, Check Variable Types

```{r load, results = FALSE, warning = FALSE, message = FALSE}
# Load data - several tables
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/Database/R_code/")
phys <- read.csv("Data/QC/LT_phys_qc.csv")
zoop_catch <- read.csv("Data/TblZoopsCatchData.csv")
zoop_ref <- read.csv("Data/TblZooplankton.csv")
zoop_tax <- read.csv("Data/YB_TaxonomyTable.csv")
wy <- read.csv("Data/WaterYearType_CDEC.csv")
# qcsamp is zoop_all (see below) but with field comments flagged. 2019 data were removed manually. Rows were added to account for comments that applied to both 150 and 50 nets. 
qcsamp <- read.csv("Data/Zoop_Field_QC.csv") 

# Add and change date formats
phys$SampleDate<-as.Date(phys$SampleDate, format ="%Y-%m-%d")
phys$Year <- ordered(year(phys$SampleDate))
phys$Month <- ordered(month(phys$SampleDate))
phys$MonthAbb <-ordered(phys$MonthAbb,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))
phys$Datetime = as.POSIXct(phys$Datetime, format = "%Y-%m-%d %H:%M:%S")

```

## 3. Clean up some columns

```{r filter, results = FALSE, message = FALSE, warning = FALSE}

# Some renaming 
zoop_ref <- zoop_ref %>%
  rename(`150_ZoopStartMeter`= X150_ZoopStartMeter,
         `50_ZoopStartMeter`= X50_ZoopStartMeter,
         `150_ZoopEndMeter`= X150_ZoopEndMeter,`50_ZoopEndMeter`= X50_ZoopEndMeter,
         `50_StartTime`= X50_StartTime,`50_StopTime`= X50_Stoptime,
         `150_SetTime`= X150SetTime,`50_SetTime`= X50_SetTime,
         `50_VolMeso` = X50_VolMeso, `50_SubMeso` = X50_SubMeso,
         `50_VolMicro` = X50_VolMicro, `50_SubMicro` = X50_SubMicro)

zoop_catch <- zoop_catch %>%
  rename(Subsample = Subsample.)

# Get rid of a few columns
zoop_catch <- zoop_catch[,c(1:3,4:6)]
phys$Date <- NULL
phys$X <- NULL
zoop_ref$X <- NULL
zoop_ref$QC_Flag <- NULL
```

## 4. Make changes that need to be made to data

```{r QC, message = FALSE, warning = FALSE}
#Organism related - change duplicates of organisms to the same Organism ID. This needs to be done in both
#taxonomy and catch tables.
zoop_catch$OrganismID[zoop_catch$OrganismID==114] <- 102
zoop_catch$OrganismID[zoop_catch$OrganismID==113] <- 95
zoop_catch$OrganismID[zoop_catch$OrganismID==66] <- 3
zoop_catch$OrganismID[zoop_catch$OrganismID==67] <- 33
zoop_catch$OrganismID[zoop_catch$OrganismID==75] <- 31
zoop_catch$OrganismID[zoop_catch$OrganismID==79] <- 9
zoop_catch$OrganismID[zoop_catch$OrganismID==71] <- 58

# Two records mislabeled as OrganismID = 68 (an old code) - change to 64
zoop_catch$OrganismID[zoop_catch$ZoopsDataID==882] <- 64
zoop_catch$OrganismID[zoop_catch$ZoopsDataID==1005] <- 64
zoop_catch <- zoop_catch %>% mutate(OrganismID = replace(OrganismID, OrganismID==68 & Year>2003, 64))
 
# Add ZoopNetType to a few 50-micron entries
zoop_catch$ZoopNetType[zoop_catch$ZoopsCatchID==8663] <- 50
zoop_catch$ZoopNetType[zoop_catch$ZoopsCatchID==8664] <- 50
zoop_catch$ZoopNetType[zoop_catch$ZoopsCatchID==8665] <- 50
zoop_catch$ZoopNetType[zoop_catch$ZoopsCatchID==9829] <- 50
zoop_catch$ZoopNetType[zoop_catch$ZoopsCatchID==10375] <- 50

# Change Flowmeter Values. Other changes have been made in database. 
zoop_ref$`50_ZoopEndMeter`[zoop_ref$ZoopsDataID==799] <- 990000
zoop_ref$`50_ZoopEndMeter`[zoop_ref$ZoopsDataID %in% c(955,968,1000)] <- 1000000

# Remove a row (incorrect duplicate data)
zoop_ref <- zoop_ref %>% filter(ZoopsDataID != 766)

# Calculate Flowdiff: difference between Start and End flowmeter
zoop_ref <- zoop_ref %>%  mutate(`150_Flowdiff` = (`150_ZoopEndMeter`-`150_ZoopStartMeter`),
    `50_Flowdiff` = (`50_ZoopEndMeter`-`50_ZoopStartMeter`))

```

## 5. Merge data tables, calculate CPUE

```{r cpue, message = FALSE, warning = FALSE}
# Merge datasets for CPUE variables
catch_zoop0 <- inner_join(zoop_ref, zoop_catch, by = "ZoopsDataID")

# Fill in "ZoopNetType" as 150 for all that are not entered
catch_zoop0$ZoopNetType[is.na(catch_zoop0$ZoopNetType)] <- 150

# Merge taxonomic tree
catch_zoop <- left_join(catch_zoop0, zoop_tax, by = "OrganismID") 
#catch_zoop <- catch_zoop0

# Calculate CPUE (Count/(S/V))
# CPUE differs based on flowmeter used, net size, and meso vs. microzooplankton
  # First calculate the volumes:
    # Volume sampled = (pi * diameter^2/4) * (Flowdiff * rotor constant/999999))
    # Subsample correction = (volume subsampled * #subsamples/ volume sent to contractors)

cz1 <- catch_zoop %>%
  mutate(`50_V_reg` = (pi*0.25/4)*(`50_Flowdiff`*26873/999999),
         `50_V_low` = (pi*0.25/4)*(`50_Flowdiff`*57560/999999),
         `150_V_reg` = (pi*0.25/4)*(`150_Flowdiff`*26873/999999),
         `150_V_low` = (pi*0.25/4)*(`150_Flowdiff`*57560/999999),
         `50_S_micro` = catch_zoop$`50_SubMicro` * catch_zoop$`Subsample`/catch_zoop$`50_VolMicro`,
         `50_S_meso`  = catch_zoop$`50_SubMeso` * catch_zoop$`Subsample`/catch_zoop$`50_VolMeso`,
         `150_S_micro` = catch_zoop$`SubMicro` * catch_zoop$`Subsample`/catch_zoop$`VolMicro`,
         `150_S_meso`  = catch_zoop$`SubMeso` * catch_zoop$`Subsample`/catch_zoop$`VolMeso`) %>%
mutate(CPUE = ifelse((ZoopNetType == 50 & FlowMeterSpeed == "Regular" & Classification == "Microzooplankton & Nauplii"), 
                            round(((Count/`50_S_micro`) /`50_V_reg`),3), 
         ifelse((ZoopNetType == 50 & FlowMeterSpeed == "Regular" & Classification != "Microzooplankton & Nauplii"), 
                round(((Count/`50_S_meso`)/`50_V_reg`),3),
         ifelse((ZoopNetType == 50 & FlowMeterSpeed == "Low" & Classification != "Microzooplankton & Nauplii"),
                round(((Count/`50_S_meso`)/`50_V_low`),3),
         ifelse((ZoopNetType == 50 & FlowMeterSpeed == "Low" & Classification == "Microzooplankton & Nauplii"),
                round(((Count/`50_S_micro`)/ `50_V_low`),3),
         ifelse((ZoopNetType == 150 & FlowMeterSpeed == "Regular" & Classification == "Microzooplankton & Nauplii"), 
                            round(((Count/`150_S_micro`) / `150_V_reg`),3), 
         ifelse((ZoopNetType == 150 & FlowMeterSpeed == "Regular" & Classification != "Microzooplankton & Nauplii"), 
                round(((Count/`150_S_meso`)/`150_V_reg`),3),
         ifelse((ZoopNetType == 150 & FlowMeterSpeed == "Low" & Classification != "Microzooplankton & Nauplii"),
                round(((Count/`150_S_meso`)/`150_V_low`),3),
         ifelse((ZoopNetType == 150 & FlowMeterSpeed == "Low" & Classification == "Microzooplankton & Nauplii"),
                round(((Count/`150_S_micro` )/ `150_V_low`),3),NA)))))))))

# Reduce duplicative variables that have a 150 and 50 entry
cz2 <- cz1 %>%
  mutate(StartTime1 = ifelse(ZoopNetType ==150, StartTime, `50_SetTime`),
         StopTime1 = ifelse(ZoopNetType == 150, StopTime, `50_StopTime`),
         SetTime = ifelse(ZoopNetType == 150, `150_SetTime`, `50_SetTime`),
         FlowMeterStart = ifelse(ZoopNetType == 150, `150_ZoopStartMeter`, `50_ZoopStartMeter`),
         FlowMeterEnd = ifelse(ZoopNetType == 150, `150_ZoopEndMeter`, `50_ZoopEndMeter`),
         VolMeso1 = ifelse(ZoopNetType == 150, VolMeso, `50_VolMeso`),
         SubMeso1 = ifelse(ZoopNetType == 150, SubMeso, `50_SubMeso`),
         VolMicro1 = ifelse(ZoopNetType == 150, VolMicro, `50_VolMicro`),
         SubMicro1 = ifelse(ZoopNetType == 150, SubMicro, `50_SubMicro`)) %>%
  select(-c(StartTime:`50_ZoopEndMeter`, VolMeso:`50_SubMicro`))

# Merge physical data
# After 2003 there was no "Other Calanoids" category but it is still being entered
zoop_all_0 <- inner_join(phys,cz2, by = "PhysicalDataID") %>% 
  mutate(OrganismID = replace(OrganismID, OrganismID==68 & Year>2003, 64))

```


# Clean up a little more 

```{r Rename and rearrange}
# Rename some columns, remove unnecessary columns
zoop_all_1 <- zoop_all_0 %>%
  dplyr::select(-c(EnteredBy:ZoopsCatchID, X, `50_V_reg`:`150_S_meso`)) %>%
  dplyr::rename(VolMicro = VolMicro1,
         SubMicro= SubMicro1,
         VolMeso= VolMeso1,
         SubMeso=SubMeso1,
         StartTime = StartTime1,
         StopTime = StopTime1,
         Date = SampleDate,
         Time = SampleTime) %>%
  arrange(Year, Date, Time, StationCode, ZoopNetType) %>%
  mutate(Flowdiff = FlowMeterEnd-FlowMeterStart)


# Rearrange columns
zoop_all_2 <- zoop_all_1[, c("PhysicalDataID", "ZoopsDataID",
                         "Date", "Year", "Month", "MonthAbb", "Datetime", "Time", "StationCode",
                         "WeatherCode", "Tide", "WaterTemperature", "Secchi", "Conductivity", "SpCnd", "pH", "DO","Turbidity",
                         "MicrocystisVisualRank", "ConditionCode", "FieldComments", "LabComments",
                         "FlowMeterSpeed", "SetTime", 
                         "FlowMeterStart", "FlowMeterEnd", "Flowdiff",
                         "VolMeso", "SubMeso", "VolMicro", "SubMicro", 
                         "Subsample", "FieldComments", "LabComments",
                         "OrganismID", "Classification", "Organism", "Phylum",
                         "Subphylum", "Class", "Subclass", "Infraclass", "Superorder", "Order",
                        "Suborder", "Infraorder", "Superfamily", "Family", "Genus", "Species",
                         "TaxonName", "TaxonRank", "CommonName", "LifeStage", "Count", "ZoopNetType", "CPUE")]

# Filter down just to SHR/STTD

zoop_all <- zoop_all_2 %>%
  filter(StationCode == "SHR" | StationCode == "STTD") %>%
  filter(Year != "2019") %>%
  drop_na(CPUE)

zoop_all$ZoopNetType <- as.factor(zoop_all$ZoopNetType)
levels(zoop_all$ZoopNetType) <- c("50_micron", "150_micron")


# Write file if you want
# write.csv(zoop_all, "R_write/zoop_merged.csv")
```


## 6a. Start QC flag process:
* Add Water Year Type - this will be used to come up with grouped averages
* QC Flags: 1 = Pass/ 3 = Suspect/ 5 = Fail & Replace Value
* Flag 1: Flowmeter Data
* Flag 2: Sampling issues
* Flag 3: CPUE

```{r Review-Add water year and other QC file}
library(mefa)

### Water Year 
# Modify water year data frame to include months for joining
wytype <- as.data.frame(rep(wy, each = 12))
wytype <- wytype %>%
  arrange(WY) %>%
  mutate(Month = ordered(rep(1:12,22))) %>%
  mutate(Year = ordered(ifelse(Month %in% c(10,11,12), WY+1, WY)))

# Add water year type
zoop_forreview_0 <- zoop_all %>%
  left_join(wytype, by = c("Year", "Month")) %>%
  select(-c(WYType, Index))

################## Flag Flowmeter data: Flag_QC1 ############################
# Mutate QC Flags and Codes for 150 data (different criteria for 150 vs 50) 
# Conditions for Flag 3: Flowdiff between 200-399, 10000-19999
# Conditions for Flag 5: Flowdiff<200, 20000+
# Codes: FMLOW/FMHIGH
zoop_forreview_150 <- zoop_forreview_0 %>%
  filter(ZoopNetType == "150_micron") %>%
  mutate(QC_Flag1 = ifelse(((Flowdiff < 400 & Flowdiff > 199) | 
                             (Flowdiff > 9999 & Flowdiff<20000)), 3, 
                    ifelse((Flowdiff <200 | Flowdiff > 19999), 5, 1))) %>%
  mutate(QC_Comment1 = ifelse(Flowdiff< 400, "FMLOW",
                              ifelse(Flowdiff > 9999 , "FMHIGH", "")))
  
# Separate table for 50 data: 100-199, 5000-9999
# Conditions for Flag 5: Flowdiff <100, 10000+
# Codes: FMLOW/FMHIGH
zoop_forreview_50 <- zoop_forreview_0 %>%
  filter(ZoopNetType == "50_micron") %>%
  mutate(QC_Flag1 = ifelse(((Flowdiff > 99 & Flowdiff < 200) |
                            (Flowdiff > 4999 & Flowdiff<10000)), 3, 
         ifelse((Flowdiff <100 | Flowdiff > 9999), 5, 1))) %>%
  mutate(QC_Comment1 = ifelse(Flowdiff< 200, "FMLOW", 
         ifelse(Flowdiff > 4999, "FMHIGH", "")))

# Merge 150-50 data
zoop_forreview_1 <- rbind(zoop_forreview_150, zoop_forreview_50)

############# Sampling Issues: Flag_QC2 #############################
# In a separate table I flagged field comments that indicated sampling issues. 
# This file is merged in. 
# See metadata for what classifies as Flag 3 vs. Flag 5
# QC Comment = SAMP
qcsamp_sub <- qcsamp %>% select(c("ZoopsDataID", "QC_Flag2", "QC_Comment2", "ZoopNetType"))
zoop_forreview_2 <- left_join(zoop_forreview_1, qcsamp_sub, by = c("ZoopsDataID", "ZoopNetType"))
zoop_forreview_2 <- zoop_forreview_2 %>%
  mutate(QC_Flag2 = replace(QC_Flag2, is.na(QC_Flag2), 1)) %>%
  mutate(QC_Comment2 = replace(QC_Comment2, is.na(QC_Comment2), ""))

zoop_forreview_2$Date <- as.Date(zoop_forreview_2$Date, format = "%m/%d/%y")

```


### 6b. Add CPUE Flag if value above upper limit
* First remove all Flags of 5 from previous two steps for calculating upper limit (ul) of CPUE outlier
* Calculate ul for outlier by WYClass, StationCode, ZoopNetType, FlowMeterSpeed
* Flag any CPUE > ul
```{r CPUE Flag}
### Calculate CPUE limits
# Remove all data with flag of 5 (Fail)
zoop_forreview_CPUE_0 <- zoop_forreview_2 %>%
  filter(QC_Flag1 != 5) %>%
  filter(QC_Flag2 != 5)

# Sum CPUE by day
CPUE_sum <- zoop_forreview_CPUE_0 %>%
  group_by(WYClass, StationCode, ZoopNetType, FlowMeterSpeed, Date) %>%
  summarize(CPUE.total = sum(CPUE))

# Which CPUE values are outliers? 
# Calculate CPUE median, quantiles, interquartile range, upper and lower limit by 
# WYClass, StationCode, ZoopNetType, FlowMeterSpeed
CPUE_quantiles <- CPUE_sum %>%
  group_by(WYClass, StationCode, ZoopNetType, FlowMeterSpeed) %>% 
  summarize(CPUE.median = median(CPUE.total),
            Q1 = quantile(CPUE.total, probs = 0.25), 
            Q3 = quantile(CPUE.total, probs = 0.75),
            IQR = Q3-Q1,
            ul = Q3 + 1.5 * IQR,
            ll = Q1 - 1.5 * IQR,
            n = n()) #%>%
  #select(-c(Q1:IQR, ll, n))


# Merge original zoop review data with quantile information
zoop_forreview_CPUE_1 <- left_join(zoop_forreview_2, CPUE_quantiles) 

########################## Flag data: QC3 ############################
# Flag if CPUE>ul
zoop_forreview_3 <-  zoop_forreview_CPUE_1 %>%
  mutate(QC_Flag3 = ifelse(CPUE>ul, 3, 1),
         QC_Comment3 = ifelse(CPUE>ul, "CPUE", "")) %>%
  select(-c(CPUE.median, ul))

############### Replace data ########################################
### Replace Flowdiffs for Flag_QC1=5
# Calculate replacement value based on initial dataset, where flags of 5 were removed 
fm_replacevals <- zoop_forreview_CPUE_0 %>%
  group_by(WYClass, StationCode, ZoopNetType, FlowMeterSpeed) %>% 
  summarize(Flowdiff.mean = round(mean(Flowdiff),0),
            Flowdiff.median = median(Flowdiff),
            Flowdiff.max = max(Flowdiff),
            n= n())

# Look at distribution to make sure it makes sense
ggplot(fm_replacevals, aes(WYClass, Flowdiff.mean, fill = FlowMeterSpeed, group = ZoopNetType)) +
  facet_wrap(~StationCode) + geom_col(position = "dodge2")

# Next, replace Flowdiff 
zoop_replace_FM <- left_join(zoop_forreview_3, fm_replacevals) %>%
  #mutate(Flowdiff = replace(Flowdiff, QC_Flag1 == 5, Flowdiff.mean[QC_Flag1 == 5]))
 mutate(Flowdiff_ed = ifelse(QC_Flag1 == 5, Flowdiff.mean, Flowdiff))

# Replace CPUE based on new Flowdiff values (new column?)
zoop_replace_CP <- zoop_replace_FM %>%
  mutate(V_reg = (pi*0.25/4)*(Flowdiff_ed*26873/999999),
         V_low = (pi*0.25/4)*(Flowdiff_ed*57560/999999),
         S_micro = SubMicro * Subsample/VolMicro,
         S_meso  = SubMeso * Subsample/VolMeso)%>%
  mutate(CPUE_ed = ifelse((FlowMeterSpeed == "Regular" & Classification == "Microzooplankton & Nauplii"), 
                            round(((Count/S_micro)/V_reg),3), 
         ifelse((FlowMeterSpeed == "Regular" & Classification != "Microzooplankton & Nauplii"), 
                round(((Count/S_meso)/V_reg),3),
         ifelse((FlowMeterSpeed == "Low" & Classification != "Microzooplankton & Nauplii"),
                round(((Count/S_meso)/V_low),3),
         ifelse((FlowMeterSpeed == "Low" & Classification == "Microzooplankton & Nauplii"),
                round(((Count/S_micro)/ V_low),3),NA))))) #%>%
  #select(-c(V_reg:S_meso))

# Check to make sure things look right
check <- zoop_replace_CP %>% select(c(Date,ZoopNetType, CPUE, CPUE_ed, Count, FlowMeterSpeed, 
                                      V_reg, V_low,S_micro, S_meso,Flowdiff, Flowdiff_ed, LabComments,QC_Flag1,
                                      Classification,TaxonName, ZoopsDataID, OrganismID)) %>%
  arrange(desc(QC_Flag1), CPUE_ed, ZoopsDataID)

# Change replaced values to flag 7
zoop_replaced <-  zoop_replace_CP %>%
  mutate(QC_Flag1 = replace(QC_Flag1, QC_Flag1 == 5, 7),
         QC_Flag3 = replace(QC_Flag3, QC_Flag1 == 7, 7),
         QC_Comment3 = replace(QC_Comment3, QC_Flag3 == 7,"FMCHANGE"))

# Change order of variables 
zoop_final <- zoop_replaced[,c("Date", "Time", "StationCode", "WeatherCode", "Tide", "WY", 
                               "WaterTemperature", "Secchi", "Conductivity", "SpCnd", "pH", 
                               "DO", "Turbidity", "MicrocystisVisualRank", "ConditionCode", "FieldComments",
                               "LabComments", "ZoopNetType", "FlowMeterSpeed", "SetTime", "FlowMeterStart", "FlowMeterEnd",
                               "Flowdiff", "Flowdiff_ed", "VolMeso", "SubMeso", "VolMicro", "SubMicro", "Subsample",
                               "OrganismID", "Classification",  "TaxonName", "TaxonRank", "CommonName", "LifeStage",
                               "Count", "CPUE", "CPUE_ed", "QC_Flag1", "QC_Comment1", "QC_Flag2", "QC_Comment2", "QC_Flag3",
                               "QC_Comment3")]
  


ggplot(zoop_replaced, aes(x = ZoopNetType, y = CPUE_ed)) +
  facet_wrap(~StationCode, scales = "free_y") + geom_col(position = "dodge2")



# Create one flag column only 
zoop_forreview_flag <- zoop_forreview_3 %>%
  mutate(QC_Flags = paste(QC_Flag1, ",", QC_Flag2, ",", QC_Flag3)) %>%
  mutate(QC_Comments = paste(QC_Comment1, ",", QC_Comment2, ",", QC_Comment3))

 


## Amount flagged
fives <- zoop_forreview_flag %>%
  filter(grepl("5", QC_Flags ))

1458/11181


```


# Summarize CPUE by sampling event/Net Type. Plot for each year.

```{r}
## Plots
ggplot(zoop_forreview, aes(Date, CPUE, col = ZoopNetType))+geom_col()

########################################################
### Summarize total CPUE and count per sampling event for 150-micron
zoop_onefifty <- zoop_forreview %>%
  filter(ZoopNetType == "150_micron")  %>%
  group_by(StationCode, WYClass, Year, Month, Date, ZoopNetType, FlowMeterSpeed, ZoopNetType, FieldComments, LabComments, QC_Flag, QC_Comment3)%>%
  summarize(ZoopsDataID = median(ZoopsDataID),
            CPUE.total = sum(CPUE),
            catch.total = sum(Count),
            Flowdiff = median(`150_Flowdiff`),
            SetTime = median(`150_SetTime`))

#### Create plots of CPUE (these go into Plots folder)

# List of all of the plots (by station)
plist <- by(zoop_onefifty, zoop_onefifty$Year, function(i) {
  p <- ggplot(i)+
    geom_point(aes(Date, CPUE.total)) +
    scale_x_date(breaks = "15 days", labels = date_format("%m/%d/%Y")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
})

# Automatically saves images in list (above) to your working directory folder.
lapply(names(plist), 
       function(x) ggsave(filename=paste("Plots/onefifty_",x,".png",sep=""), plot=plist[[x]], bg = "transparent"))


##################################################
### Summarize CPUE per sampling event for 50-micron
########################################################
### Summarize CPUE per sampling event  for 150-micron
zoop_fifty <- zoop_forreview %>%
  filter(ZoopNetType == "50_micron")  %>%
  group_by(StationCode, Year, Month, Date, WYClass, ZoopNetType, FlowMeterSpeed, ZoopNetType, FieldComments, LabComments,
           QC_Flag, QC_Comment3)%>%
  summarize(ZoopsDataID = median(ZoopsDataID),
            CPUE.total = sum(CPUE),
            catch.total = sum(Count),
            Flowdiff = median(`50_Flowdiff`),
            SetTime = median(`50_SetTime`))


#### Create plots of CPUE (these go into Plots folder)
# List of all of the plots (by station)
plist2 <- by(zoop_fifty, zoop_fifty$Year, function(i) {
  p2 <- ggplot(i)+
    geom_point(aes(SampleDate, CPUE.total)) +
    scale_x_date(breaks = "15 days", labels = date_format("%m/%d/%Y")) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
})

# Automatically saves images in list (above) to your working directory folder.
lapply(names(plist2), 
       function(x) ggsave(filename=paste("Plots/fifty_",x,".png",sep=""), plot=plist2[[x]], bg = "transparent"))
```

* Calculate mean, sd, median, IQR, ul, ll for each Year/Station/FlowMeterSpeed Combo.
* QC_Flag = 3 Suspect, 5 Fail + Replaced, 1 Pass
* QC_Comments = "FMLOW" Flowmeter difference low "FMHIGH" Flowmeter difference high,
* "CPUE" CPUE "SAMP" Sampling issue 
* CPUE: ul = Quantile3 + 1.5*IQR for station, year, flowmeterspeed combo.
* For 150_micron: FM<401|FM>9999|CPUE>UL suspect FM <201|FM>19999 Fail
* For 50_micron: FM<201|FM>5000|CPUE>UL suspect FM<101|FM>9999 Fail

```{r Flag data with high CPUE}


###################### 150 micron ################################
##################################################################

### Calculate median, IQR
onefifty.medians <- zoop_onefifty %>%
  group_by(StationCode, WYClass, FlowMeterSpeed, ZoopNetType) %>%
  summarize(CPUE.median = median(CPUE.total),
            Q1 = quantile(CPUE.total, probs = 0.25), 
            Q3 = quantile(CPUE.total, probs = 0.75),
            IQR = Q3-Q1,
            ul = Q3 + 1.5 * IQR,
            ll = Q1 - 1.5 * IQR,
            CPUE.mean = mean(CPUE.total),
            SD.CPUE = sd(CPUE.total),
            Flowdiff.mean = mean(Flowdiff),
            SD.Flowdiff = sd(Flowdiff),
            n = n())

### Join sample data with medians and mark "check" for anything over the upper limit or below CPUE of 200
onefiftycheck <- left_join(zoop_onefifty, onefifty.medians) %>%
  mutate(QC_Flag = ifelse(CPUE.total > ul | (Flowdiff <400 & Flowdiff > 199) | (Flowdiff > 9999 & Flowdiff<20001), "-1", 
                          ifelse(Flowdiff <200 | Flowdiff > 19999, "-2", "")),
         QC_Comment1 = ifelse(CPUE.total>ul, "CPUE", ""),
         QC_Comment2 = ifelse(Flowdiff<401, "FMLOW", 
                              ifelse(Flowdiff > 9999, "FMHIGH", ""))) %>%
  dplyr::select(-c(Q1,Q3, SD.CPUE, CPUE.mean))


################# 50 Micron #######################
###################################################

### Calculate median, IQR for 50-zoop net
fifty.medians <- zoop_fifty %>%
  group_by(StationCode, WYClass, FlowMeterSpeed, ZoopNetType) %>%
  summarize(CPUE.median = median(CPUE.total),
            Q1 = quantile(CPUE.total, probs = 0.25), 
            Q3 = quantile(CPUE.total, probs = 0.75),
            IQR = Q3-Q1,
            ul = Q3 + 1.5 * IQR,
            ll = Q1 - 1.5 * IQR,
            CPUE.mean = mean(CPUE.total),
            SD.CPUE = sd(CPUE.total),
            Flowdiff.mean = mean(Flowdiff),
            SD.Flowdiff = sd(Flowdiff),
            n = n())

### Join sample data with medians and mark "check" for anything over the upper limit or below CPUE of 100
fiftycheck <- left_join(zoop_fifty, fifty.medians) %>%
  mutate(QC_Flag = ifelse(CPUE.total > ul | (Flowdiff <200 & Flowdiff > 99) | (Flowdiff > 4999 & Flowdiff<10001), "-1", 
                          ifelse(Flowdiff <100 | Flowdiff > 4999, "-2", "")),
         QC_Comment1 = ifelse(CPUE.total>ul, "CPUE", ""),
         QC_Comment2 = ifelse(Flowdiff<200, "FMLOW", 
                              ifelse( Flowdiff > 4999, "FMHIGH", ""))) %>%
  dplyr::select(-c(Q1,Q3,ll, SD.CPUE, CPUE.mean))
```


## 12. Replace flagged values
```{r Replacement}

### Read in file with flags

zoop_flags <- read.csv("Checkzoopoutliers3.csv")

### Merge in flag, replace, mean, median values with zooplankton data

zoop_replace <- merge(zoop_all, checkoutliers) # Merge zooplankton data with the relevant mean and median values
zoop_replace_flag <- merge(zoop_replace, zoop_flags, by = "ZoopsDataID") # Merge data with flag and replace columns
zoop_flag_merge$Replace[is.na(zoop_flag_merge$Replace)] <- "N" # For data not in outlier files, fill "Replace" column with "N" 

### Replace incorrect values
# New column of flowdiffs. If replace = N, flowdiff does not change. If replace = Y, replace with the mean. 
zoop_edited <- zoop_flag_merge %>%
  mutate(Flowdiff2 = ifelse(Replace == "Y", Mean.CPUE, Flowdiff))

```


## Include variables relevant to EDI. 
```{r EDI/Public}

# zoop_pub <- zoop_forreview %>%
#   dplyr::select(-c(FlowMeterSpeed:`50_SetTime`, ZoopsDataID)) %>%
#   arrange(Date, Time, StationCode)

#write.csv(zoop_pub, "R_write/Zoop_public.csv")


# EDI/Public

zoop_edi_catch <- zoop_edited %>%
  select(-c(`150_Flowdiff`, `50_Flowdiff`, ZoopsDataID)) %>%
  arrange(SampleDate, SampleTime, StationCode, ZoopNetType)

# Write file if you want
write.csv(zoop_edi_catch_2,"R_write/yolo_zoop_public.csv")
```








## 7a. Overview of data: net differences

```{r Organisms Plot, echo = FALSE, message = FALSE, warning = FALSE}

# Net type and year
ggplot(zoop_all, aes(Year, CPUE, fill = ZoopNetType)) + geom_col()

# Make some datasets
calanoid <- zoop_cpue %>% filter(Order == "Calanoida")
cladocera <- zoop_cpue %>% filter(Suborder == "Cladocera")
cyclopoid <- zoop_cpue %>% filter(Order == "Cyclopoida")
macro <- zoop_cpue %>% filter(Classification == "Macrozooplankton")
micro <- zoop_cpue %>% filter(Classification == "Microzooplankton & Nauplii")

# Look at organisms - CPUE 
ggplot(zoop_cpue, aes(x=Classification, y = CPUE, fill =NetType)) + 
  geom_col(position = "dodge") +
    scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) + labs(title = "Classification")+
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11),axis.title.x = element_blank(),axis.text.x = element_text(angle = 90, hjust = 1)) 

```

## 7b. Look at organisms by taxonomic categories
```{r Organisms Plot big, warning = FALSE, message = FALSE, fig.width=12, fig.height=16}

# Look at each taxonomic category
t1 <- ggplot(zoop_cpue, aes(x=Phylum, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="Sum CPUE by Phylum") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11),axis.title.x = element_blank(),
                    axis.text.x = element_text(angle = 90, hjust = 1)) 

t2 <- ggplot(zoop_cpue, aes(x=Class, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="Sum CPUE by Class") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11),axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

t3 <- ggplot(zoop_cpue, aes(x=Subclass, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="Sum CPUE by SubClass") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11),axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

zoop_order <- zoop_cpue %>%
  filter(!is.na(Order))
t4 <- ggplot(zoop_order, aes(x=Order, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="CPUE by Order") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11),axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

zoop_family <- zoop_cpue %>%
  filter(!is.na(Family))
t5 <- ggplot(zoop_family, aes(x=Family, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="CPUE by Family") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 9), axis.title = element_text(size = 11),axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

zoop_genus <- zoop_cpue %>%
  filter(!is.na(Genus))
t6 <- ggplot(zoop_genus, aes(x=Genus, y = CPUE, fill = NetType)) + geom_col(position = "dodge") + labs(title="CPUE by Genus") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 8), axis.title = element_text(size = 11),axis.title.x = element_blank(),axis.text.x = element_text(angle = 90, hjust = 1)) 

# Compare changes: Organism vs.Taxon
# Calanoid species
org1 <- ggplot(calanoid, aes(x=Organism, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") + labs(title = "Calanoid - Organism") +  
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

tax1 <- ggplot(calanoid, aes(x=TaxonName, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") + labs(title = "Calanoid - Taxon") +  
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

# Cladocera species
org2 <- ggplot(cladocera, aes(x=Organism, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Cladocera - Organism")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

tax2 <- ggplot(cladocera, aes(x=TaxonName, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Cladocera - Taxon")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 
# Cyclopoid species
org3 <- ggplot(cyclopoid, aes(x=Organism, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  labs(title = "Cylopoid - Organism")+
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

tax3 <- ggplot(cyclopoid, aes(x=TaxonName, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  labs(title = "Cylopoid - Taxon")+
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1)) 

# Macrozooplankton
org4 <- ggplot(macro, aes(x=Organism, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Macrozooplankton - Organism")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1))

tax4 <- ggplot(macro, aes(x=TaxonName, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Macrozooplankton - Taxon")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1))

# Microzooplankton
org5 <- ggplot(micro, aes(x=Organism, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Microzooplankton - Organism")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1))

tax5 <- ggplot(micro, aes(x=TaxonName, y = CPUE, fill = NetType)) + 
  geom_col(position = "stack") +
  labs(title = "Microzooplankton - Taxon")+
  scale_fill_manual(values=c("#f0aa37", "#b3dfa2")) +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11), axis.title.x = element_blank(),
                     axis.text.x = element_text(angle = 90, hjust = 1))

grid.arrange(t1, t2, t3, t4, t5, t6, ncol = 2)
grid.arrange(org1, org2, org3, org4, org5, ncol = 2)
grid.arrange(tax1, tax2, tax3, tax4, tax5, ncol = 2)
```




### ANOVAs
```{r ANOVA}
library(car)

################# STTD ##################
### Plot data
zoop_150_sttd <- zoop_onefifty %>%
  filter(CPUE.total < 3000000) %>%
  filter(StationCode == "STTD") %>%
  mutate(Flowdiff_s = Flowdiff/SetTime)

zoop_150_sttd_reg <- zoop_150_sttd %>%
    filter(FlowMeterSpeed == "Regular")

zoop_150_sttd_low <- zoop_150_sttd %>%
    filter(FlowMeterSpeed == "Low")

# CPUE plots
ggplot(zoop_150_sttd_reg, aes(Year, CPUE.total))+geom_boxplot()

# Flowdiff/settime plots
ggplot(zoop_150_sttd_reg, aes(Year, Flowdiff_s))+geom_boxplot()


### Run ANOVAs
sttd.aov.cp.r <- aov(CPUE.total~Year, data = zoop_150_sttd_reg)
summary(sttd.aov.cp.r)

TukeyHSD(sttd.aov.cp.r)

####### CPUE Zoop_150_STTD_Reg #######
### Run ANOVAs
sttd.aov.cp.r <- aov(CPUE.total~Year, data = zoop_150_sttd_reg)
summary(sttd.aov.cp.r)

TukeyHSD(sttd.aov.cp.r)

### Check assumptions
# Homogeneity of variances
plot(sttd.aov.cp.r, 1)
leveneTest(CPUE.total ~ Year, data = zoop_150_sttd_reg)

  # Normality
plot(sttd.aov.cp.r, 2)
sttd_residuals_cp_r <- residuals(object = sttd.aov.cp.r)
shapiro.test(x = sttd_residuals )

######## Flowdiff Zoop_150_STTD_Reg #######

### Run ANOVAs
sttd.aov.f.r <- aov(Flowdiff_s~Year, data = zoop_150_sttd_reg)
summary(sttd.aov.f.r)

TukeyHSD(sttd.aov.f.r)

### Check assumptions

  # Homogeneity of variances
plot(sttd.aov.f.r, 1)
leveneTest(Flowdiff_s ~ Year, data = zoop_150_sttd_reg)

  # Normality
plot(sttd.aov.f.r, 2)
sttd_residuals_f_r <- residuals(object = sttd.aov.f.r)
shapiro.test(x = sttd_residuals_f_r)

######## CPUE Zoop_150_STTD_Low #######

ggplot(zoop_150_sttd_low, aes(Year, CPUE.total))+geom_boxplot()
ggplot(zoop_150_sttd_low, aes(Year, Flowdiff_s))+geom_boxplot()

### Run ANOVAs
sttd.aov.cp.l <- aov(CPUE.total~Year, data = zoop_150_sttd_low)
summary(sttd.aov.cp.l)

TukeyHSD(sttd.aov.cp.l)

### Check assumptions

  # Homogeneity of variances
plot(sttd.aov.cp.l, 1)
leveneTest(CPUE.total ~ Year, data = zoop_150_sttd_low)

  # Normality
plot(sttd.aov.cp.l, 2)
sttd_residuals_cp_l <- residuals(object = sttd.aov.cp.l)
shapiro.test(x = sttd_residuals_cp_l)

######## Flowdiff Zoop_150_STTD_Low #######

### Run ANOVAs
sttd.aov.f.l <- aov(Flowdiff_s~Year, data = zoop_150_sttd_low)
summary(sttd.aov.f.l)

TukeyHSD(sttd.aov.f.l)

### Check assumptions

  # Homogeneity of variances
plot(sttd.aov.f.l, 1)
leveneTest(Flowdiff_s ~ Year, data = zoop_150_sttd_low)

  # Normality
plot(sttd.aov.f.l, 2)
sttd_residuals_f_l <- residuals(object = sttd.aov.f.l)
shapiro.test(x = sttd_residuals_f_l)

################# SHR ##################

zoop_shr <- zoop_onefifty %>%
  filter(CPUE.total < 1000000)%>%
  filter(StationCode == "SHR")%>%
  filter(FlowMeterSpeed == "Low") %>%
  mutate(Flowdiff_s = Flowdiff/SetTime)

ggplot(zoop_shr, aes(Year, CPUE.total)) + geom_boxplot()
ggplot(zoop_shr, aes(Year, Flowdiff_s)) + geom_boxplot()

### Run ANOVA
shr.aov <- aov(Flowdiff_s~Year, data = zoop_shr)
summary(shr.aov)

TukeyHSD(shr.aov)
### Check assumptions

  # Homogeneity of variances
plot(shr.aov, 1) 
leveneTest(CPUE.total ~ Year, data = zoop_shr)

  # Normality
plot(shr.aov, 2)
shr_residuals <- residuals(object = shr.aov)
shapiro.test(x = shr_residuals )

### Kruskal-Wallis
kruskal.test(CPUE.total~Year, data = zoop_shr)


```


## 9. Look at Flowmeter data

```{r Flow, message = FALSE, warning = FALSE}

# Remove rows with no flowdiff value
Flowmeter <- zoop_all %>%
  gather(`150_Flowdiff`, `50_Flowdiff`, key = "NetType", value = "Flowdiff") %>%
  filter(!is.na(Flowdiff)) %>%
  filter(!is.na(FlowMeterSpeed))

# Histogram by net type
ggplot(Flowmeter, aes(Flowdiff)) + geom_histogram(binwidth = 500) +
  facet_wrap(~NetType) + theme_bw()

# Look at flow values by month
Flow_yr_month <- Flowmeter %>%
  group_by(NetType, Year, MonthAbb) %>%
  select(NetType,Year,MonthAbb,Flowdiff) %>%
  summarize(max.flow = max(Flowdiff),
            median.flow = median(Flowdiff),
            min.flow = min(Flowdiff))

# Look at flow values by month
Flow_month <- Flowmeter %>%
  group_by(NetType,MonthAbb) %>%
  summarize(max.flow = max(Flowdiff),
            median.flow = median(Flowdiff),
            min.flow = min(Flowdiff))

# Boxplots
ggplot(Flowmeter, aes(MonthAbb, Flowdiff)) + 
  geom_boxplot(fill = "#26bb11") + labs(title = "Boxplot: All Flows") + theme_bw() + facet_wrap(~NetType)

ggplot(Flow_yr_month, aes(MonthAbb, median.flow)) + geom_boxplot(fill = "#00acee") + 
  facet_wrap(~NetType) +labs(title = "Boxplot: Median flow over multiple years") + theme_bw()

# List of all flow diferences by station and date
Flow_sta_comments <- Flowmeter %>%
  filter(StationCode %in% c("STTD", "SHR")) %>%
  select(ZoopsDataID, StationCode, Year, SampleDate, MonthAbb, NetType, Flowdiff, FieldComments) %>%
  group_by(ZoopsDataID, StationCode, NetType,Year, SampleDate, MonthAbb, Flowdiff, FieldComments) %>%
  arrange(StationCode,NetType,Year,SampleDate,Flowdiff) %>%
  distinct(SampleDate,StationCode)

```

## 10. Calculate summary stats and IQR for flowmeter readings

```{r IQR Flowmeter}

# Calculate median, MAD, lower and upper ranges for each day
Flow.sum <- Flowmeter %>%
  filter(StationCode == "STTD" | StationCode == "SHR") %>%
  group_by(StationCode, NetType, FlowMeterSpeed) %>%
   summarize(min.Flowdiff = min(Flowdiff),
             max.Flowdiff = max(Flowdiff))

# Calculate median, MAD, lower and upper ranges for each day
Flow.IQR <- Flowmeter %>%
  filter(StationCode == "STTD" | StationCode == "SHR") %>%
  group_by(StationCode, NetType, FlowMeterSpeed) %>%
   summarize(Q1 = quantile(Flowdiff, probs = 0.25), 
            Q3 = quantile(Flowdiff, probs = 0.75),
            IQR = Q3-Q1,
            ul = Q3 + 1.5 * IQR,
            ll = Q1 - 1.5 * IQR)
kable(Flow.sum) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

kable(Flow.IQR) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

## 11. Read dayflow data
```{r incorporate dayflow}

dayflow <- read.csv("Data/Flow/Yolo_dayflow_compiled.csv")

# Extract date from flow dataset
dayflow <- dayflow %>%
  rename(SampleDate = Date) %>%
#mutate(Day = substr(Date, start = 1, stop = 2)) %>%
  #mutate(SampleDate = (paste(Year, Mo, Day, sep = "-"))) %>%
  arrange(Year)

dayflow$SampleDate <- as.Date(dayflow$SampleDate, format = "%Y-%m-%d")
dayflow$Month <- ordered(month(dayflow$SampleDate))
dayflow$Year <- ordered(dayflow$Year)
dayflow$Day <- as.character(day(dayflow$SampleDate))

# Look at flow data
ggplot(dayflow, aes(SampleDate, Flow)) + 
  geom_point()

ggplot(dayflow, aes(Month, Flow)) + 
  geom_boxplot()

# There are several repeats
dayflowF <- dayflow %>%
  distinct(SampleDate, .keep_all = TRUE)

# Combine 50-150 CPUE outliers with dayflow. 
checkoutliers <- rbind(fiftycheck,onefiftycheck)
checkoutliers$Day <- as.character(day(checkoutliers$SampleDate))
checkoutliers2 <- left_join(checkoutliers, dayflowF) %>%
  arrange(StationCode, SampleDate) %>%
  dplyr:: select(-c(Day, X, Mo, check, IQR, ll))

# Write outliers file
write.csv(checkoutliers2, "R_write/Checkzoopoutliers.csv")

```

